О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-23 pps-linear-bound/pps-linear-lower-bound.tex
Proper reference to construction
Grant notice

On existence and diameter bounds of integral point sets.

@@

Summing up the construction 1 above and~\cite[lemma 3 and proposition 6]{our-vmmsh-2018},
we obtain the following

>>>>

On existence and diameter bounds of integral point sets.
\footnote{
	This work was carried out at Voronezh State University and supported by the Russian Science
	Foundation under grant 19-11-00197.
}

@@

Summing up Construction~\ref{con:planar_set_with_minimeter_1} above and~\cite[lemma 3 and proposition 6]{our-vmmsh-2018},
we obtain the following
